\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\geometry{left=1in, right=1in, top=1in, bottom=1in}

\titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\large\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    \textbf{\huge Nirek Shetty}\\
    Passionate Programmer, Team Member, Leader, and Teacher, Driven To Bring The Best I Can To Wherever Life Takes Me.
\end{center}

\begin{center}
    Toronto, M2N 2C8 \\
    647 - 346 - 4162 \\
    \href{mailto:shettynirek@gmail.com}{shettynirek@gmail.com} \\
    \href{https://github.com/nirek13}{github.com/nirek13} \\
    \href{https://nirekshetty.tech}{nirekshetty.tech}
\end{center}

\section*{EXPERIENCE}

\subsection*{Satellite Campus, Hackathon Team, Toronto}
\textit{December 2023 - PRESENT}\\
\begin{itemize}[leftmargin=*]
    \item Youngest member of a team ranked Top 40 in the world by NASA.
    \item Represented the team in nationwide competitions, demonstrating adaptability by acquiring and implementing diverse skills on short notice.
    \item Sponsorship and pitching Co-Lead winning an award at my first competition.
    \item Pitched innovative ideas to distinguished judges, industry experts and even the City Councillor of Milton, ON.
\end{itemize}

\subsection*{Hackathons Canada 501 (c)(3) Non Profit, Founding Member}
\textit{January 2024 - PRESENT}\\
\begin{itemize}[leftmargin=*]
    \item Proud member and Co-Builder of the Canadian Hackers Website.
    \item Instrumental in the exponential growth of our community, witnessing an increase from a few individuals to nearly 1,000 in a matter of months.
    \item Acquired substantial real-world experience in pitching innovative ideas to industry leaders, including successful engagements with companies like Microsoft and HCB.
    \item Co-Led a team and orchestrated collaboration among multiple teams working under firm deadlines, showcasing effective leadership and teamwork skills.
\end{itemize}

\subsection*{Mind Over Matter Karate, Martial Arts Instructor}
\textit{November 2021 - PRESENT}\\
\begin{itemize}[leftmargin=*]
    \item Passionately taught kids the principles of self-defense, emphasizing values such as perseverance, mental and physical strength, humility, and the transformation of emotions into productivity.
    \item Acquired valuable leadership skills and extensive experience working with younger kids and motivating them to push past their limits.
\end{itemize}

\subsection*{Buffoons Team \#22544, First Tech Canada, Team Lead}
\textit{September 2023 - December 2023}\\
\begin{itemize}[leftmargin=*]
    \item Served as the leader of my team, playing pivotal roles in delivering pitches to judges, programming our entire bot, networking with other teams, and overseeing overall team management.
    \item Led the team in devising innovative and unconventional ideas, securing a 2nd Place Design Award and highlighting a commitment to creative problem-solving and constant innovation.
\end{itemize}

\section*{PROJECTS}

\subsection*{Demeter AI}
This is my upcoming submission to the GenAI hackathon run by the D\(^3\) Institute from Harvard hosted at Microsoft HQ. The purpose of this project is to process DNA primer strips to recognize and taxonomically classify organisms providing farmers with comprehensive treatments which not only would improve the farmers crop yield but have huge spillover effects into daily life and society.

\subsection*{Cat Smasher}
Embark on a whimsical gaming adventure with our retro-inspired Pong rendition. Picture this: one player, armed with a motion controller, engages in a lively duel against an unbeatable AI opponent. The twist? Instead of the conventional ball, players find themselves gleefully bashing a cat around the screen. The atmosphere is set with unbelievably cheery music, creating a blend of classic gameplay, motion control antics, and humor. Get ready for a gaming experience that's not only entertaining but also delightfully quirky! 🥇 - Halton Hacks Best Rookie Hack

\subsection*{RedLeaf Finance}
RedLeaf Finance was the finance app I created when I was just ten years old. It enabled users to buy, sell, obtain quoted prices, check their holdings, and view their losses and profits. While it may not be the most impressive project I've ever undertaken, I decided to include it on the list due to the sheer personal pride I felt upon its completion. This project holds special significance for me as it played a pivotal role in sparking my passion for programming and ultimately led me to be who I am today.

\textbf{These are just a few of the projects I have created thus far and I invite you to view a more complete collection of these projects at \href{https://github.com/nirek13}{https://github.com/nirek13}}

\section*{SKILLS}
\begin{itemize}[leftmargin=*]
    \item Fluent In Most Major Programming Languages
    \item Lots of Experience With Machine Learning Algorithms
    \item Quick Study And Able To Learn New Technologies Quickly
    \item Lots Of Marketing And Pitching Experience
    \item Real World Leadership And Team Collaboration Skills
\end{itemize}

\section*{AWARDS AND ACHIEVEMENTS}
\begin{itemize}[leftmargin=*]
    \item 3RD Rank In Canadian National Math Contest Thale Against Nearly 7,000 Participants
    \item Best Rookie Hack At Halton Hacks Inaugural Event
    \item Certificate Of Achievement From Canadian National Fluid Power Association
    \item 2ND Place Design Award FTC Mississauga Event
    \item 3RD Place Connect Award FTC Bolton Event
    \item Finished Harvard Cs50 At Ten Years Old
    \item WMS Award for Excellences in The Sciences ‘20
    \item Honour Roll Student At Brebeuf College School
    \item 5x Time Waterloo Distinction Winner
    \item Pascal Contest School Champion
    \item Won Silver+ at OBA a provincial band association with an invitation to Nationals
\end{itemize}

\end{document}
